Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2016-11-26 paper.tex
Typo

Model selection is one of the most computationally expensive tasks in
machine learning applications. When dealing with kernel methods for structures,
the choice with the largest impact on the overall performance is the selection
of the feature bias, i.e. the choice of the concrete kernel for structures.
Each kernel in turn exposes several hyper-parameters which also need to be
fine tuned. Finally, the downstream learning algorithm has its own hyper-
parameters. A common approach to hyper-parameters optimization is to fix
a-priori  a \textit{parameters grid}, i.e. a set of possible values for each
parameter. Then, the predictive performance of the learning algorithm is
evaluated for each possible parameters combination ({\em grid-search}
strategy), which is possibly a very time consuming step.  A more efficient
approach has been proposed in~\cite{FabioAiolliMicheleDonini2015,Massimo2016},
where instead of selecting the best parameters configuration, Multiple Kernel
Learning (MKL) was used for combining different kernel matrices in a single
learning procedure. While more efficient, this approach does not scale to very
large datset since a kernel matrix has to be computed for each kernel and for
each of its hyper-parameters. In this paper we propose a new approach that,
based on sub-sampling and MKL, is able to speedup the parameter selection
phase by orders of magnitude on real-world datasets  without loss in
predictive performance.

@@

These algorithms are supported by several theoretical results that bound the \emph{estimation error} (i.e. the difference between the true error and the empirical margin error). These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Cortes2009c}%,Hussain2011,Hussain2011a}. %,Kakade2009,Micchelli2005,Kloft2012,Srebro2006,

>>>>

Model selection is one of the most computationally expensive tasks in
machine learning applications. When dealing with kernel methods for structures,
the choice with the largest impact on the overall performance is the selection
of the feature bias, i.e. the choice of the concrete kernel for structures.
Each kernel in turn exposes several hyper-parameters which also need to be
fine tuned. Finally, the downstream learning algorithm has its own hyper-parameters. A common approach to hyper-parameters optimization is to fix
a-priori  a \textit{parameters grid}, i.e. a set of possible values for each
parameter. Then, the predictive performance of the learning algorithm is
evaluated for each possible parameters combination ({\em grid-search}
strategy), which is possibly a very time consuming step.  A more efficient
approach has been proposed in~\cite{FabioAiolliMicheleDonini2015,Massimo2016},
where instead of selecting the best parameters configuration, Multiple Kernel
Learning (MKL) was used for combining different kernel matrices in a single
learning procedure. While more efficient, this approach does not scale to very
large datset since a kernel matrix has to be computed for each kernel and for
each of its hyper-parameters. In this paper we propose a new approach that,
based on sub-sampling and MKL, is able to speedup the parameter selection
phase by orders of magnitude on real-world datasets  without loss in
predictive performance.

@@

These algorithms are supported by several theoretical results that bound the \emph{estimation error} (i.e. the difference between the true error and the empirical margin error). These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Cortes2009c}.%,Hussain2011,Hussain2011a}. %,Kakade2009,Micchelli2005,Kloft2012,Srebro2006,
